Exploratory Plots

### 2020-05-28 exploratory/2020/README.Rmd
Use functions

---
title: "plots.Rmd"
author: "Kelly Sovacool"
date: "5/27/2020"
output: 
  github_document:
    html_preview: false
---

@@

# Fitting datasets to a reference database vs _de novo_ clustering

```{r fit_db_sensspec}
sensspec <- read_tsv(here('subworkflows/2_fit_reference_db/results/merged.sensspec')) %>% 
  mutate(method=fct_relevel(method, c("open", "closed", "de_novo")))
sensspec %>% group_by(dataset, method) %>% 
  ggplot(aes(x=method, y=mcc, fill=dataset)) +
  geom_jitter()
```

```{r fit_db_benchmarks}
benchmarks <- read_tsv(here('subworkflows/2_fit_reference_db/results/benchmarks.txt')) %>% 
  mutate(method=fct_relevel(method, c("open", "closed", "de_novo")))
benchmarks %>% group_by(dataset, method) %>% 
  ggplot(aes(x=method, y=s, fill=dataset)) +
  geom_jitter() +
  labs(y='seconds')
```

>>>>

---
title: "Exploratory Plots"
date: "5/27/2020"
output: 
  github_document:
    html_preview: false
---

@@

# Fitting datasets to a reference database vs _de novo_ clustering
```{r functions}
relevel_method <- function(df) {
  df %>%
    mutate(method = fct_relevel(method, c("open", "closed", "de_novo")))
}
plot_jitter <- function(df, y) {
  df %>% group_by(dataset, method) %>% 
      ggplot(aes(x=method, y={{ y }}, fill=dataset)) +
  geom_jitter()
}
```

```{r fit_db_sensspec}
sensspec <- read_tsv(here('subworkflows/2_fit_reference_db/results/merged.sensspec')) %>% 
  relevel_method()
sensspec %>% 
  plot_jitter(mcc)
```

```{r fit_db_benchmarks}
benchmarks <- read_tsv(here('subworkflows/2_fit_reference_db/results/benchmarks.txt')) %>% 
  relevel_method
benchmarks %>% 
  plot_jitter(s) +
  labs(y='seconds')
```
